# 1. BUSINESS UNDERSTANDING
## a. Defining the question
## b. Defining the metric of success
## c. Understading the context
## d. Recording the experimental design
## e. Data Relevance
## f. Appropriateness of the data
# 2. DATA AQUISITION AND EXTRACTION, TRANSFORMING AND LOADING
## a. Importing of the libraries
```{r}
library(data.table)
```
### Reading the data
```{r}
part12 <- fread('http://bit.ly/CarreFourDataset')
part3 <- fread('http://bit.ly/SupermarketDatasetII')
part4 <- fread('http://bit.ly/CarreFourSalesDataset')
```
```{r}
head(part12,10)
```
```{r}
tail(part12,10)
```

```{r}
head(part12,10)
```

```{r}
head(part4,10)
```
```{r}
tail(part4,10)
```
```{r}
part3 <- fread('http://bit.ly/SupermarketDatasetII' , sep= ':', header = FALSE)
```

```{r}
head(part3, 10)
```
```{r}
tail(part3,10)
```
```{r}
cat('The first datasets dimentions are:')
print(dim(part12))
cat('\n')
cat('The first datasets dimentions are:')
print(dim(part3))
cat('\n')
cat('The first datasets dimentions are:')
print(dim(part4))
cat('\n')
```

```{r}
part12$Total == part4$Sales
```

```{r}
part12$Date == part4$Date
```
### Understanding the data

```{r}
majinazacolumns <- colnames(part12)
typesofcolumndata <- c()
uniquenoofelements <- c()
for (qw in majinazacolumns){
  typesofcolumndata <- c(typesofcolumndata, class(part12[[qw]]))
  uniquenoofelements <- c(uniquenoofelements, length(unique(part12[[qw]])))
}

desc <- data.frame(
  'Column Names' = majinazacolumns,
  'Column Type' = typesofcolumndata,
  'Number of unique' = uniquenoofelements
)
desc
```
### Outliers

### Anomalies
### Missing data 
# 3. EXPLORATORY DATA ANALYSIS
### Univariate 
### Bivariate
### Multivariate
# 4. Insights
# 5. Conclusion
# 6. Recommendation